Mental simulation as Bayesian Quadrature

### 2013-05-31 man/nips-2013.tex
Add some todos, include Tom's feedback

We considered three metrics of performance in particular:
\begin{itemize}
\item \textit{Responses}: How accurate was the model at choosing the
  correct hypothesis? This was defined to be the mean error ($\ME{}$),
  or fraction of times the model picks the incorrect hypothesis.
\item \textit{Rotations}: For those ``same'' pairs which the model
  judged correct, how correlated were the model's rotations with the
  true angles of rotation?  We quantified this using the Pearson's
  correlation coefficient $\rho$ for $R$ vs. $\vert
  \mathbf{R}\vert$. The top row in Figure \ref{fig:rotations} shows
  individual points corresponding to true rotations vs. rotations by
  the models for all stimuli, including those judged incorrectly. The
  bottom row shows mean model rotations, across only those stimuli
  which were judged correctly. We structured the analysis in this way
  to better compare to the results of \cite{Shepard1971}, which also
  excluded incorrectly judged stimuli.
\item \textit{Estimates of $Z$}: How accurate was the model's estimate
  of $Z$? We defined this quantity as the mean squared error
  ($\MSE{}$) between the model's estimate of $Z$ and the ``gold
  standard'' value, where the error has scale such that $\MSE{}=0$
  indicates no error and $\MSE{}=1$ indicates maximum error. Figure
  \ref{fig:accuracy} shows plots of the true (``gold standard'') value
  of $Z$ vs. the model's estimate, for each model.
\end{itemize}

@@

The \naive{} model's response error rate was better than chance, with
$\NaiveME{}$. Closer inspection reveals that much of this comes from
``different'' pairs ($\NaiveMEdiff{}$), where the asymmetric linear
interpolation may give an overestimate of $Z$ (e.g. Figure
\ref{fig:li}).  This intuition is confirmed by the model's accuracy
($\NaiveMSE{}$) in estimating $Z$: as shown in the left panel of
Figure \ref{fig:accuracy}, it overestimated for nearly all stimuli
pairs.

@@

The parametric model's error in determining whether the objects were
identical was $\VMME{}$, making more errors on ``same'' pairs
($\VMMEsame{}$) than ``different'' pairs ($\VMMEdiff{}$). Rather than
overestimating as with the \naive{} model, however, the parametric
model largely underestimated $Z$. This is unsurprising: because the
Von Mises distribution only has a single peak, it necessarily
underestimates $Z$ for multimodal similarity functions. Overall, the
parametric model had an error rate of $\VMMSE{}$ in estimating $Z$,
which was significantly more accurate than that of the \naive{} model.

@@

The nonparametric model was much more accurate in choosing the correct
hypothesis than the other two models ($\BQME{}$). We note that this is
very close to the 3.2\% error rate reported by \cite{Shepard1971},
though further experimentation is necessary to determine whether the
types of errors people make align with those of the model.

The average rotations computed by the nonparametric model were
strongly correlated with the true rotations ($\BQcorr$, see Figure
\ref{fig:rotations}, bottom right). Because the nonparametric model
has the capacity to ``restart'', it could recover from rotating in the
incorrect direction (e.g. Figure \ref{fig:bq}) and thus did not
over-rotate as frequently.  It also under-rotated less frequently:
because the model continues to rotate until it is confident that its
estimate of $Z$ is accurate, it does not get stuck as easily on local
optima.  Indeed, its active attempts to obtain an accurate estimate of
$Z$ were largely succeessful, with $\BQMSE{}$.

>>>>

We considered three metrics of performance in particular:
\begin{itemize}
\item \textit{Response error rates}: How accurate was the model at
  choosing the correct hypothesis? This was defined to be the mean
  error ($\ME{}$), or fraction of times the model picks the incorrect
  hypothesis.
\item \textit{Rotations}: For those ``same'' pairs which the model
  judged correct, how correlated were the model's rotations with the
  true angles of rotation?  We quantified this using the Pearson's
  correlation coefficient $\rho$ for the true rotation ($R$) versus
  the extent of the model's rotations ($\vert \mathbf{R}\vert$). The
  top row in Figure \ref{fig:rotations} shows individual points
  corresponding to true rotations vs. rotations by the models for all
  stimuli, including those judged incorrectly. The bottom row shows
  mean model rotations, across only those stimuli which were judged
  correctly. We structured the analysis in this way to better compare
  to the results of \cite{Shepard1971}, which also excluded
  incorrectly judged stimuli.
\item \textit{Estimates of $Z$}: How accurate was the model's estimate
  of $Z$? We defined this quantity as the mean squared error
  ($\MSE{}$) between the model's estimate of $Z$ and the ``gold
  standard'' value, where the error has scale such that $\MSE{}=0$
  indicates no error and $\MSE{}=1$ indicates maximum error. Figure
  \ref{fig:accuracy} shows plots of the true (``gold standard'') value
  of $Z$ vs. the model's estimate, for each model.
\end{itemize}

@@

The \naive{} model's response error rate was $\NaiveME{}$, which is
better than chance (equivalent to guessing randomly,
i.e. $\ME{}=0.5$). \TODO{binomial test?} Closer inspection reveals
that much of this comes from ``different'' pairs ($\NaiveMEdiff{}$),
where the asymmetric linear interpolation may give an overestimate of
$Z$ (e.g. Figure \ref{fig:li}).  This intuition is confirmed by the
model's accuracy in estimating $Z$, which was $\NaiveMSE{}$. As shown
in the left panel of Figure \ref{fig:accuracy}, it overestimated $Z$
for nearly all stimuli pairs. \TODO{how many?}

@@

The parametric model's error in determining whether the objects were
identical was $\VMME{}$, making more errors on ``same'' pairs
($\VMMEsame{}$) than ``different'' pairs ($\VMMEdiff{}$). \TODO{is
  this significant?} Rather than overestimating as with the \naive{}
model, however, the parametric model largely underestimated $Z$. This
is unsurprising: because the Von Mises distribution only has a single
peak, it necessarily underestimates $Z$ for multimodal similarity
functions. Overall, the parametric model had an error rate of
$\VMMSE{}$ in estimating $Z$, which was significantly more accurate
than that of the \naive{} model \TODO{test}.

@@

The nonparametric model was much more accurate in choosing the correct
hypothesis than the other two models ($\BQME{}$) \TODO{test}. We note
that this is very close to the 3.2\% error rate reported by
\cite{Shepard1971}, though further experimentation is necessary to
determine whether the types of errors people make align with those of
the model.

The average rotations computed by the nonparametric model were
strongly correlated with the true rotations ($\BQcorr$, see Figure
\ref{fig:rotations}, bottom right). Because the nonparametric model
has the capacity to ``reset'', it could recover from rotating in the
incorrect direction (e.g. Figure \ref{fig:bq}) and thus did not
over-rotate as frequently.  It also under-rotated less frequently:
because the model continues to rotate until it is confident that its
estimate of $Z$ is accurate, it does not get stuck as easily on local
optima.  Indeed, its active attempts to obtain an accurate estimate of
$Z$ were largely succeessful, with $\BQMSE{}$.
